\textls[-0]{\thetitle}

### 2023-03-23 lang-design.tex
edits

As an example, consider the substitution function "subst", defined using
\lsti!FRecursion!.
The \lsti{on} clause specifies that recursion is over "tm".
The \lsti{motive} clause suggests that the recursive function being
defined has type \lsti{tm -> id -> tm -> tm}.
%
The "subst" function in "STLC" is further bound by the "subst" in "STLCFix":
the four cases from "STLC" are automatically inherited and reused,
with "STLCFix" retroactively adding a fifth case to form the new "subst" function.
%
For exhaustivity, it is a static error if the programmer fails to
further bind "subst" and define this fifth case.
The type system does this check in family \lsti{STLCFix}
by examining if the inductive type "tm",
over which "subst" is recursively defined, is further bound in the same family.

>>>>

As an example, consider the substitution function "subst", defined using
\lsti!FRecursion!.
The \lsti{on} clause specifies that recursion is over "tm".
The \lsti{motive} clause suggests that the recursive function being
defined has type \lsti{tm -> id -> tm -> tm}.
%
The "subst" function in "STLC" is further bound by the "subst" in "STLCFix":
the four cases from "STLC" are automatically inherited and reused,
with "STLCFix" adding a fifth case retroactively to form a new "subst" function.
%
For exhaustivity, it is a static error if the programmer fails to
further bind "subst" and define this fifth case.
The type system does this check in family \lsti{STLCFix}
by examining if the inductive type "tm",
over which "subst" is recursively defined, is further bound in the same family.

### 2023-03-23 metatheory-condensed.tex
revamp figure 8
edits

\definecolor{A-color}{HTML}{E7EFC5}
\definecolor{T-color}{HTML}{FFF1D0}
\definecolor{t-color}{HTML}{FAE0E4}

@@

We use \cref{fig:stlc-linkage-typing} to illustrate.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
\mathit{self} : A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
The context types $A_i$ are a dependent tuple type, but for readability,
we write them as dependent record types that give labels to the fields.
Field accesses are notated, for example, $\getfield{\mathit{self}}{"tm"}$.
%we use a notation with explicit names
%in this typing judgment:
%we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
%and write its type~$A_i$, which is a dependent tuple type, as a
%dependent record type with labels.
%
\begin{itemize}
% [leftmargin=4ex,itemsep=.5ex]
  [labelsep=*,leftmargin=1pc,itemsep=3pt]

@@

In rules \ruleref{l/add} and \ruleref{lsig/add},
the third premise $\goodTerm{\Gm,x : \TyTkg{\lsig}}{\seal}{A}$ is
responsible for hiding W-type signatures.
Here, $\TyTkg{\lsig}$ packages $\lsig$---recall that $\lsig$ contains the
(self-parameterized) types of all the fields preceding the current
field~$t$---into a dependent tuple type (\ruleref{tyeq/pk/add}).
The term $\seal$ turns a tuple of type $\TyTkg{\lsig}$ into a new tuple of type~$A$
that hides W-type signatures behind $\cU$, if necessary.
%
It is straightforward to find the~$\seal$ that fits the bill, though this process
is not automated in \TT.
In particular, when no hiding is needed, $\seal$ is simply~$x$,
%\EDJ{$\var{0}$ is not identity (substitution), but the first variable, right? Or you meant to say it is identity ``sealing''?}\YZreply{Yes, I meant identity sealing. I cannot say 'sealing' because the paper currently does not use the word sealing anywhere.}\EDJreply{What about just remove the parenthesis and ``the identity''}
and $A$ is $\TyTkg{\lsig}$.
In \cref{fig:stlc-linkage-typing}, $\seal_1$, $\seal_2$, and $\seal_{10}$ are simply $x$,
and $\seal_6$ has the typing
\begingroup
\fontsize{9}{9}\selectfont%
\goodTerm{
  x :
  \big[\texttt{tm} : \TyS{\wcode{\wsig_{\texttt{tm}}}},\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
}{
  \seal_6
}{
  \big[\texttt{tm} : \cU,\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
}.
\endgroup

>>>>

\definecolor{A-color}{HTML}{E7EFC5}
\definecolor{T-color}{HTML}{FFF1D0}
\definecolor{t-color}{HTML}{FAE0E4}
\definecolor{P-color}{HTML}{BFEFFF}

@@

We use \cref{fig:stlc-linkage-typing} to illustrate.
On the left is code excerpted from \cref{fig:stlc-mechanized}, and on the right
is how the corresponding fields are modeled and typed in \TT.
%
$\lkg_i$ is the linkage that adds the $i$-th field~$t_i$ with the typing
$\goodTerm{%
\tikzmarkin[disable rounded corners=true,set fill color=A-color,set border color=A-color]{A-i}(-0.02,-0.10)(-0.02,0.28)
\mathit{self} : A_i%
\tikzmarkend{A-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=t-color,set border color=t-color]{t-i}(-0.02,-0.10)(-0.02,0.28)%
t_i%
\tikzmarkend{t-i}%
}{%
\tikzmarkin[disable rounded corners=true,set fill color=T-color,set border color=T-color]{T-i}(-0.02,-0.10)(-0.02,0.28)%
T_i%
\tikzmarkend{T-i}%
}$.
%
The context types $A_i$ are a dependent tuple type, but for readability,
we write them as dependent record types that give labels to the fields.
Field accesses are notated, for example, as $\getfield{\mathit{self}}{"tm"}$.
%we use a notation with explicit names
%in this typing judgment:
%we name the context as $\mathit{self}$ (cf.~\cref{fig:stlc-compiled})
%and write its type~$A_i$, which is a dependent tuple type, as a
%dependent record type with labels.
%
\begin{itemize}
% [leftmargin=4ex,itemsep=.5ex]
  [labelsep=*,leftmargin=1pc,itemsep=3pt]

@@

In rules \ruleref{l/add} and \ruleref{lsig/add},
the third premise $\goodTerm{\Gm,x : \TyTkg{\lsig}}{\seal}{A}$ is
responsible for hiding W-type signatures.
Here, $\TyTkg{\lsig}$ packages $\lsig$---recall that $\lsig$ contains the
(self-parameterized) types of all the fields preceding the current
field~$t$---into a dependent tuple type (\ruleref{tyeq/pk/add}).
The term $\seal$ turns a tuple of type $\TyTkg{\lsig}$ into a new tuple of type~$A$
that hides W-type signatures behind $\cU$, if necessary.\footnote{%
In the presence of hiding, it is important that the context type~$A$ be a
dependent tuple type rather than a linkage type; we expand on this issue in an
appendix.}
%
It is straightforward to find the~$\seal$ that fits the bill, though this process
is not automated in \TT.
In particular, when no hiding is needed, $\seal$ is simply~$x$,
%\EDJ{$\var{0}$ is not identity (substitution), but the first variable, right? Or you meant to say it is identity ``sealing''?}\YZreply{Yes, I meant identity sealing. I cannot say 'sealing' because the paper currently does not use the word sealing anywhere.}\EDJreply{What about just remove the parenthesis and ``the identity''}
and $A$ is $\TyTkg{\lsig}$.
In \cref{fig:stlc-linkage-typing}, $\seal_1$, $\seal_2$, and $\seal_{10}$ are simply $x$,
while $\seal_6$ hides $"tm" : \TyS{\wcode{\wsig_{\texttt{tm}}}}$
as $"tm" : \cU$ in $A_6$
so that the typing of~$t_6$ is oblivious to the concrete signature
$\wsig_{\texttt{tm}}$ and therefore can be reused.
%\begingroup
%\fontsize{9}{9}\selectfont%
%\goodTerm{
%  x :
%  \big[\texttt{tm} : \TyS{\wcode{\wsig_{\texttt{tm}}}},\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}{
%  \seal_6
%}{
%  \big[\texttt{tm} : \cU,\ \texttt{tm\_unit} : \El{\texttt{tm}},\ \dadada\big]
%}.
%\endgroup
